---
title: "Working with APIs"
author: "Showroop Pokhrel"
date: "12/2/2018"
output:
  html_document: default
  word_document: default
---

In this project, I make the use of Functional Programming in R to:
1. Use the Le Monde API (a leading French newspaper) to search and retrieve specific news articles from the Le Monde database.
2. Convert relevant articles from French to English by calling the Google Translate API 
3. Convert the translated files from text to speech using Google Text-to-Speech API


## Preliminaries
You need to have your Gcloud API key before starting. Watch this [video](https://www.youtube.com/watch?v=1JNwpp5L4vM) on getting your API credentials. 
```{r}
library(httr, quietly = T)
library(DescTools, quietly = T)

#Global Constants
#Le Monde API key
api_key <- "9f7b1e42e3dc4e8ca0796fe89c431083"
#GCloud API key
cloud_api_key <- "AIzaSyBbUbtvJ3BZp7ryicOgIu5EwPkBMtk5Zfc"
base <-  "https://newsapi.org/v2/"
```


## 1. Retriving most recent articles given a certain keyword
This function returns a dataframe containing articles published in the the past month in Le Monde and filtered for particular keyword(s). I used the span of a month b/c the API only provides access to articles dating back a month from today's date
```{r, results="hold"}
get_last_month_articles_by_keywords <- function(source="le-monde", keywords){
  date.today <- Sys.Date()
  last.month <- DescTools::AddMonths(date.today, -1)
  prefix <- "everything?q="
  keyword <- paste(keywords, collapse = "&")
  query <- paste(prefix, keyword,"&from=", last.month, "&sources=",source, sep="")
  url <- paste(base, query, "&apiKey=", api_key, sep="")
  x <- httr::GET(url=url) #Get me the info associated with this url
  x <- jsonlite::fromJSON(rawToChar(x$content))
  return(x$articles)
}
```

Example: Querying for articles that mention "Trump" and "Saudi" together
```{r, results="hold"}
df <- get_last_month_articles_by_keywords(source ="le-monde" ,c("trump","saudi"))
knitr::kable(df[1:5,2:4], caption = "A subset of the dataframe containing articles published in Le Monde that mentioned Trump and Saudi together")
```



## 2. Retrieving most recent headlines from Le Monde
This function returns most recent headlines from Le Monde. The keyword parameter is set as optional. If a keyword is specified, it will filter for most recent headlines containing that particular keyword
```{r, results="hold"}
get_headlines <- function(source="le-monde", keyword){
  prefix <- "top-headlines?"
  
  #Making keyword an optional parameter
  if(missing(keyword)){
    query <- paste(prefix, "sources=",source, sep="")
  }
  else{
    keyword <- paste(keyword, collapse = "&")
    query <- paste(prefix, "q=",keyword, "&sources=", source, sep="")
  }

  url <- paste(base, query,"&apiKey=", api_key, sep="")
  x <- httr::GET(url=url)
  x <- jsonlite::fromJSON(rawToChar(x$content))
  return(x$articles$title)
} 
```

Usage:
```{r, results="hold"}
headline <- get_headlines()
headline
```



## 3. Translation from French to English
Given a vector of sentences in French (hence source=="fr"), this function translates it into English (target="en") by calling the Google Translate API
```{r, results="hold"}
translate <- function(text, source="fr", target="en", cloud_api_key = "AIzaSyBbUbtvJ3BZp7ryicOgIu5EwPkBMtk5Zfc"){
  translated <- rep(NA,length(text))
  base <- "https://translation.googleapis.com/language/translate/v2?key="
  url <- paste(base, cloud_api_key, sep="")
  
  for ( i in 1: length(text)){
  body <- paste("{",
                "'q':'", text[i], "',", 
              "'source':'", source, "',",
              "'target':'", target, "',",
              "'format':'text',",  
              "}", sep="")
  x <- httr::POST(url, body = body)
  x <- jsonlite::fromJSON(rawToChar(x$content))
  translated[i] <- x$data$translations$translatedText
  }
  return(translated)
}
```

Usage
```{r, results="hold"}
headline.eng <- translate(headline)
headline.eng
```


## 3. Converting French Text to Speech
Given a text in French, this function internally calls the system and translates it into speech
```{r, results="hold"}
text_to_speech <- function(text, cloud_api_key="AIzaSyBbUbtvJ3BZp7ryicOgIu5EwPkBMtk5Zfc"){
  text <- paste(text, collapse=" ")
  text <- gsub("'", "", text)
  input <- paste("'input':{'text':'", text, "'}", sep="")
  voice <- "'voice':{'languageCode':'fr-FR','name':'fr-FR-Standard-A','ssmlGender':'FEMALE'}"
  output <- "'audioConfig':{'audioEncoding':'MP3'}"

  s_body <- paste("{", input, ",", voice, ",", output, "}", sep="")

  base_url <- "https://texttospeech.googleapis.com/v1/text:synthesize?key="
  url <- paste(base_url, cloud_api_key, sep="")
  x <- httr::POST(url, body = s_body)
  x <- jsonlite::fromJSON(rawToChar(x$content))
  
  Sys.setenv(output_string=x$audioContent)
  system("echo $output_string > sound_out.txt")

  system("base64 --decode sound_out.txt > sound_out.mp3")
  system("afplay sound_out.mp3")
  return(NULL)
}

#text_to_speech(headline)

```




